File-based localization of numerical perturbations in data analysis pipelines

### 2020-04-01 paper.tex
Edited results section

Two types of differences are observed: between-process and between-subject.
Between-process differences occur when the same tool behaves differently in different process instances.
For example, \texttt{flirt}
always produces files without differences in the \texttt{AAve} sub-pipeline but 
almost always creates different files in the \texttt{AAli} sub-pipeline.
Conversely, the same process can be reproducible for some subjects but not for others.

@@

To visually illustrate the observed differences,
Figure~\ref{fig:fnirt_result} compares FNIRT results in Brain Extraction
for a particular subject. Differences appear to be very substantial, in
particular in the frontal and parietal lobes. 
\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{images/t2w_alignment.png} 
    \caption{Differences between FNIRT results in PreFreeSurfer's Brain Extraction (CentOS6 vs. 
    CentOS7) \tristan{Improve contrast}. An animated version of the comparison is available 
    \href{https://github.com/ali4006/HCP-reproducibility-paper/blob/master/images/pfs_t2w_alignment.gif}
    {here}.
} 
    \label{fig:fnirt_result}
\end{figure}

@@

The only non-reproducible process identified in FreeSurfer was
\texttt{mris\_make\_surfaces}, which was the case for 10 out of 20
subjects. \tristan{do you know why this was the case: is this CLI
dynamically linked? Ali: It includes dynamic linking and I guess it may be affected by this.} 
This process generates the cortical and white matter
surfaces. However, this does not mean that FreeSurfer results were
identical for the remaining 10 subjects and for the other processes, due to the
propagation of PreFreeSurfer differences.

For instance, Figure~\ref{fig:tissue_class} illustrates the sum of
binarized between-OS differences among the 20 whole-brain segmentations. An
animated comparison of the segmentations obtained in 1 subject is available
\href{https://github.com/ali4006/HCP-reproducibility-paper/blob/master/images/fs_brain_segmentation.gif}
{here}.

The Dice coefficients associated with the 44 regions segmented by
FreeSurfer are shown in Figure~\ref{fig:scatter_plot}. This figure shows
high Dice coefficients (more than 0.95) in large regions and very low Dice
coefficients (below 0.5) in small structures particularly in the vessels
and lateral ventricles.

\begin{figure}
%  \includegraphics{brain\_classification}
\centering
  \includegraphics[width=\columnwidth]{images/brain_segmentation_mni.png} 
  \caption{Sum of binarized between-OS differences between whole-brain FreeSurfer segmentations (N=20),
           resampled and overlaid to the MNI152 volume template.
} 
  \label{fig:tissue_class}
\end{figure}

\begin{figure*}
  \centering
    \includegraphics[width=\textwidth]{images/scatter_plot.png} 
    \caption{The scatter plots of the Dice coefficients between segmented regions 
            from 20 subjects in FreeSurfer (CentOS6 vs. CentOS7). 
            The x-axes are the number of voxels in each region and 
            y-axes are Dice values that are in different scales in two plots.
            The right plot shows the similarity between regions larger than $10^4$ voxels. 
            The left plot represents the differences between 
            regions smaller than $10^4$ voxels.
            The complete table of Dice coefficient values is 
            \href{https://github.com/ali4006/HCP-reproducibility-paper/blob/master/data/dice_values.csv}
            {available}.} 
    \label{fig:scatter_plot}
  \end{figure*}

@@

The reproducibility of a given tool may vary across subjects, and across parameters. 
See FLIRT in DC in Figure 4.

>>>>

@@

To visually illustrate the observed differences,
Figure~\ref{fig:fnirt_result} compares FNIRT results in Brain Extraction
for a particular subject. Differences appear to be very substantial, in
particular in the frontal and parietal lobes. 
\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{images/t2w_alignment.png} 
    \caption{Differences between T2 FNIRT results in PreFreeSurfer's Brain Extraction (CentOS6 vs 
    CentOS7) \tristan{Improve contrast}. An animated version of the comparison is available 
    \href{https://github.com/big-data-lab-team/HCP-reproducibility-paper/blob/master/images/pfs_t2w_alignment.gif}
    {here}.
} 
    \label{fig:fnirt_result}
\end{figure}

@@

The only non-reproducible process identified by \toolname in FreeSurfer was
\texttt{mris\_make\_surfaces} (cortical and white matter surfaces
generation), which is also the only dynamically-linked executable in this pipeline
\tristan{Ali, could you check that this is indeed the only dynamic
executable in the pipeline?}. \texttt{mris\_make\_surfaces} produced different results for
10 out of 20 subjects.

While by design \toolname only identifies processes that create
differences between conditions, pipeline results may still differ due to
the propagation and amplification of differences created at previous
processing steps, PreFreeSurfer in our case. We observed the effect of this
propagation in FreeSurfer results, as shown in
Figure~\ref{fig:tissue_class} for whole-brain segmentations. Furthermore,
the Dice coefficients associated with the 44 regions segmented by
FreeSurfer are shown in Figure~\ref{fig:scatter_plot}, showing low Dice
values (below 0.5) in the smallest structures.

\begin{figure}
%  \includegraphics{brain\_classification}
\centering
  \includegraphics[width=\columnwidth]{images/brain_segmentation_mni.png} 
  \caption{Sum of binarized differences between whole-brain FreeSurfer
  segmentations obtained from PreFreeSurfer processings in CentOS6 vs CentOS7
   (N=20). Segmentations were resampled and overlaid to the MNI152 volume
  template. An animated comparison of segmentations obtained for a particular subject is available
\href{https://github.com/big-data-lab-team/HCP-reproducibility-paper/blob/master/images/fs_brain_segmentation.gif}
{here}.
} 
  \label{fig:tissue_class}
\end{figure}

\begin{figure*}
  \centering
  \begin{subfigure}{0.45\linewidth}
    [FIGURE GOES HERE]
    \caption{Regions with \emph{less} than 10,000 voxels.}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.45\linewidth}
    [FIGURE GOES HERE]
    \caption{Regions with \emph{more} than 10,000 voxels.}
  \end{subfigure}
    % \includegraphics[width=\textwidth]{images/scatter_plot.png} 
    \caption{Dice coefficients between regions segmented by FreeSurfer in CentOS6 vs CentOS7 (N=20).
        To improve readability, the two graphs are on different y scales. \tristan{Ali, could you separate the figures in 2 and insert them in each subfigure?}} 
    \label{fig:scatter_plot}
  \end{figure*}

@@

Static vs dynamic executables

The reproducibility of a given tool may vary across subjects, and across parameters. 
See FLIRT in DC in Figure 4.
Two types of differences are observed: between-process and between-subject.
Between-process differences occur when the same tool behaves differently in different process instances.
For example, \texttt{flirt}
always produces files without differences in the \texttt{AAve} sub-pipeline but 
almost always creates different files in the \texttt{AAli} sub-pipeline.
Conversely, the same process can be reproducible for some subjects but not for others.
